Order Preserving Encryption Schemes: \\ Preventing the Leakage of Distribution\\ 6.857 Final Paper \\ Hrishikesh Joshi, Max Kolysh, Mari Miyachi, John Wang

### 2013-05-07 paper.tex
Working on DCS scheme for the paper.

@@

  Consider a simple tie-breaking rule on top of Popa et al (2013)'s mOPE scheme. When the client inserts a new ciphertext $c^*$ into the server, the client proceeds normally when the ciphertext $c_i$ returned by the server does not correspond to a plaintext $p_i$ which is equal to $p^* = Dec(SK, c^*)$. However, if $p_i = p^*$, then the client tells the server to move left or right with uniform probability.

@@

  \subsection{Equivalence of RTOPE and DCS}

  In order to show that RTOPE and DCS are equivalent, we first need a notion of equivalence for an OPE scheme. Since both RTOPE and DCS are randomized, we cannot take the naive approach and say that two schemes are equivalent if they provide the same OPE encodings. Instead, we will use a notion of the equivalence of the distributions of the encodings. Formally, we define equivalence as follows:

@@

>>>>

\section{Distribution Confidentiality Scheme}

In order to solve the problem of leaking the distribution of the plaintext values, we have developed the Distribution Confidentiality Scheme (DCS). This scheme uses Raluca et al (2013)'s original mOPE scheme, but adds an additional layer of security.

In essence, the DCS scheme adds random bits to the end of a plaintext so that the ciphertext values are randomized. This will prevent the server from being able to identify the number of times a repeated plaintext value is inserted.

\subsection{Description of DCS}

This section will give a formal description of DCS. We will first describe the basic version of the scheme, then we will augment it so that decimal numbers can be represented as well.

In the basic version of the scheme, let us assume that we want to encrypt some plaintext value $x \in \mathrm{Z}$ and send it to the server like in Raluca et al (2013)'s mOPE scheme. For DCS, there is an additional parameter $\rho$ which will govern the probability with which the server sees a repeated value. We will generate a random value $r \in [0,1)$ which contains $\rho$ bits, denoted $r_{\rho}$, and append it to the end of $x$. The resulting value $x' = x + r_{\rho}$ will be encrypted with DET. Raluca et al (2013)'s mOPE scheme will work the same as before, but now acting on $x'$.

When the client attempts to query for $x$, he must perform a range query for $[x, x+1)$ on the server.

\subsection{Querying Under DCS}

@@

  Consider a simple tie-breaking rule on top of Popa et al (2013)'s mOPE scheme. When the client inserts a new ciphertext $c^*$ into the server, the client proceeds normally when the ciphertext $c_i$ returned by the server does not correspond to a plaintext $p_i$ which is equal to $p^* = Dec(SK, c^*)$. However, if $p_i = p^*$, then the client tells the server to move left or right with uniform probability. Note that in this scheme, we will use a randomized encryption scheme so that the server cannot tell if two plaintext values are the same.

@@

\section{Equivalence of DCS and RTOPE}

  In order to show that RTOPE and DCS are equivalent, we first need a notion of equivalence for an OPE scheme. Since both RTOPE and DCS are randomized, we cannot take the naive approach and say that two schemes are equivalent if they provide the same OPE encodings. Instead, we will use a notion of the equivalence of the distributions of the encodings. We will now formally define equivalence.

  \subsection{Equivalence}

@@

  \subsection{Equivalence of DCS and RTOPE}
